### 2023-06-20 RFCs/HDF5_Library/VFD_Subfiling/user_guide/appendices/ref_manual.tex
Update Subfiling User's Guide with notes about stripe count

\texttt{int64\_t stripe\_size} - This field contains the size (in bytes) of data stripes
written to subfiles. The default setting for this parameter is a 32MiB stripe size. The value
must be $> 0$.

\texttt{int32\_t stripe\_count} - This field contains the target number of subfiles to use.
The default setting for this parameter is set such that one subfile is used per machine node.
The value must be $> 0$.
\end{flushleft}%

@@

\texttt{int32\_t thread\_pool\_size} - This field contains the number of worker threads to
use per I/O Concentrator. The default setting for this parameter is 4 worker threads per I/O
Concentrator. The value must be $> 0$.
\end{flushleft}%

>>>>

\texttt{int64\_t stripe\_size} - This field contains the size (in bytes) of data stripes
written to subfiles. The default setting for this parameter is a 32MiB stripe size. The value
set must either be the value defined by the \texttt{H5FD\_SUBFILING\_DEFAULT\_STRIPE\_SIZE}
macro, or an integer value $> 0$.

\texttt{int32\_t stripe\_count} - This field contains the target number of subfiles to use.
It is mostly useful when pre-creating an HDF5 file in a parallel application within some
subset of \texttt{MPI\_COMM\_WORLD} (see section \ref{sec:tips}). The default setting for
this parameter is set such that one subfile is used per machine node. The value set must
either be the value defined by the \texttt{H5FD\_SUBFILING\_DEFAULT\_STRIPE\_COUNT} macro,
or an integer value $> 0$.
\end{flushleft}%

@@

\texttt{int32\_t thread\_pool\_size} - This field contains the number of worker threads to
use per I/O Concentrator. The default setting for this parameter is 4 worker threads per I/O
Concentrator. The value set must either be the value defined by the \texttt{H5FD\_IOC\_DEFAULT\_THREAD\_POOL\_SIZE}
macro, or an integer value $> 0$.
\end{flushleft}%

### 2023-06-20 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/acknowledgements.tex
Update Subfiling User's Guide with notes about stripe count

% Include this section in the table of contents
\addcontentsline{toc}{section}{Acknowledgements}
This work was supported by the Exascale Computing Project (17-SC-20-SC), a collaborative effort of the U.S. Department of Energy Office of Science and the National Nuclear Security Administration.

>>>>

% Include this section in the table of contents
\addcontentsline{toc}{section}{Acknowledgements}
This work was supported by the Exascale Computing Project (17-SC-20-SC), a joint project of the U.S. Department of Energy’s Office of Science and National Nuclear Security Administration, responsible for delivering a capable exascale ecosystem, including software, applications, and hardware technology, to support the nation’s exascale computing imperative.

### 2023-06-20 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/tips.tex
Update Subfiling User's Guide with notes about stripe count

\section{Tips and best practices}

@@

>>>>

\section{Tips and best practices}
\label{sec:tips}

@@

\item If using the Subfiling VFD with a parallel HDF5 application that
pre-creates an HDF5 file on a single MPI rank or some other subset of
\texttt{MPI\_COMM\_WORLD}, it is necessary to adjust the "stripe count" (or
number of subfiles) value that the Subfiling VFD uses internally in order to
ensure that the proper number of subfiles gets generated when the logical HDF5
file is created. Without setting this value, the VFD will default to creating
one subfile per machine node, which will cause it to create only one subfile
in the case of pre-creating an HDF5 file on a single MPI rank. Note that as
pre-creating an HDF5 file on a subset of \texttt{MPI\_COMM\_WORLD} is expected
to be a less common operation when using the Subfiling VFD, an environment
variable for modifying this value has not been provided at this time and the
VFD will need to be configured on a File Access Property List for this use case.
Using the example in section \ref{ex:ex2} as a guide, one can configure the
stripe count value by setting the \texttt{stripe\_count} field in the
\texttt{H5FD\_subfiling\_params\_t} structure, which is part of the
\texttt{H5FD\_subfiling\_config\_t} structure that is passed to 
\texttt{H5Pset\_fapl\_subfiling}. For that particular example, one would
set the \texttt{subf\_config.shared\_cfg.stripe\_count} field to the desired
total number of subfiles.

### 2023-06-20 RFCs/HDF5_Library/VFD_Subfiling/user_guide/sections/usage.tex
Update Subfiling User's Guide with notes about stripe count

>>>>

Note that modifying the stripe count from its default setting is expected to be a less common operation
with the Subfiling VFD. Therefore, an environment variable for changing the value has not currently
been provided at this time. If an HDF5 application needs to modify the stripe count value (refer to
section \ref{sec:tips} for information on when modifying the stripe count value is necessary), the
Subfiling VFD will need to be configured by a File Access Property List. However, note that any
settings in environment variables will still take precedence, even when the VFD is configured by
a File Access Property List.
